### 2025-03-07 paper-reviews/papers-2025.tex
Add pathologies of big data paper

>>>>

\section*{Performance}
\begin{itemize}
    \item \cite{Jacobs:DataBasePerformance:2009}:

    The article highlights optimization challenges that database developers face while working on big data analysis. The author demonstrates performance drawbacks of reading large databases for different kind of analyses. The article is largely focused on efficient usage of hardware capabilities: random vs. sequential access to storage devices. There is a good diagram that compares random and sequential accesses of hard drives, SSDs and DRAM. The author also shows few possible database architecture focusing on possible read requests that are supposed to be serviced by the database. There is also a good definition of "big data" in the very end of the paper.
\end{itemize}
